A geographic routing approach for IPv6 in large-scale low-power and lossy networks

### 2015-04-06 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
footnote added

Our main contribution in this paper is to propose a modification into RPL protocol, in order to better support P2P communication. The proposed technique intend to integrate a geographic routing algorithm in the RPL protocol to reduce the amount of control message required for P2P communication.\removed{We further propose that} Such a routing protocol can be used\rev{, for example,} in a smart street lighting system \removed{based on IPv6-enabled} wireless \removed{sensor}network for supporting diverse applications in an urban IoT. This paper is organized as follows: Section \ref{secRequirements} addresses the requirements of a wireless sensor network to implement an smart street lighting network. Also, we argue about the benefits of creating a network with such coverage for other public services. Section \ref{sec6LoWPAN} presents an overview of the 6LoWPAN protocol, describing succinctly its operating modes, routing strategies and main drawbacks. In section \ref{secGeographicRouting} we address the geographic routing technique, highlighting its pros and cons. In section \ref{secGeoRank}, the \textit{GeoRank} algorithm is presented, depicting its working principle. We evaluate, by simulation, the performance of the proposed algorithm in Section \ref{secSimulation}. Finally, we conclude this paper in Section \ref{secConclusion}.

>>>>

Our main contribution in this paper is to propose a modification into RPL protocol, in order to better support P2P communication. The proposed technique intend to integrate a geographic routing algorithm in the RPL protocol to reduce the amount of control message required for P2P communication.\removed{We further propose that} Such a routing protocol can be used\rev{, for example,} in a smart street lighting system \removed{based on IPv6-enabled} wireless \removed{sensor}network for supporting diverse applications in an urban IoT. \footnote{\rev{Throughout the text we have used the smart street lighting as an example of application where the proposed protocol could be used, however it was not specifically designed for a street lighting system, and thus might not fulfill all the requirements for such use.}} This paper is organized as follows: Section \ref{secRequirements} addresses the requirements of a wireless sensor network to implement an smart street lighting network. Also, we argue about the benefits of creating a network with such coverage for other public services. Section \ref{sec6LoWPAN} presents an overview of the 6LoWPAN protocol, describing succinctly its operating modes, routing strategies and main drawbacks. In section \ref{secGeographicRouting} we address the geographic routing technique, highlighting its pros and cons. In section \ref{secGeoRank}, the \textit{GeoRank} algorithm is presented, depicting its working principle. We evaluate, by simulation, the performance of the proposed algorithm in Section \ref{secSimulation}. Finally, we conclude this paper in Section \ref{secConclusion}.
